---
title: "Proportion of red beads"
author: "Jack Xu"
format: html
execute: 
  echo: false
---


```{r}
#| message: false
library(tidyverse)
library(tidymodels)
library(broom)
library(marginaleffects)
```

**Logistic Model Formula**

$$
\log\left(\frac{\mathbb{P}(Y=1)}{1 - \mathbb{P}(Y=1)}\right) = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_p X_p
$$

**Evalutated**

$$
\log\left(\frac{\hat{\mathbb{P}}(Y=1)}{1 - \hat{\mathbb{P}}(Y=1)}\right) = -0.6633 + 0.5421 \cdot \text{shovel\_size} - 0.2314 \cdot \text{color\_intensity}
$$

**Converted to Probability**

$$
\hat{\mathbb{P}}(Y=1) = \frac{1}{1 + e^{-(-0.6633 + 0.5421 \cdot \text{shovel\_size} - 0.2314 \cdot \text{color\_intensity})}}
$$

```{r}
shovel <- tibble(
  color = factor(c(
    "red", "white", "white", "red", "red", "white", "white", "white", "white", "white",
    "white", "white", "white", "red", "red", "red", "white", "white", "red", "white",
    "white", "white", "white", "white", "red", "white", "red", "white", "red", "white",
    "white", "red", "red", "white", "white", "white", "white", "white", "white", "white",
    "red", "red", "red", "white", "white", "red", "white", "red", "white", "white"
  ))
)
```

```{r}
#| cache: true
fit_color <- logistic_reg(engine = "glm") %>%
  fit(color ~ 1, data = shovel)
```

```{r}
# Create the tidy output with confidence intervals
library(broom)
tidy_output <- tidy(fit_color, conf.int = TRUE)

# Option 2: Using the gt package for a more styled table
library(gt)
tidy_output %>%
  gt() %>%
  tab_header(
    title = "Logistic Regression Coefficients",
    subtitle = "Includes Confidence Intervals"
  ) %>%
  tab_source_note(
    source_note = "Source: Logistic regression estimates from a shovel sample of beads drawn from an urn"
  )
```

```{r}
plot_predictions(fit_color,
                 type = "prob",
                 condition = "group") +
  labs(
    title = "Predicted Probability of Bead Color in Shovel Samples",
    subtitle = "Based on Logistic Regression Model",
    x = "Bead Color",
    y = "Predicted Probability",
    caption = "Data source: Shovel sampling from urn beads experiment"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 18),
    plot.subtitle = element_text(size = 14, color = "gray40"),
    axis.title = element_text(face = "bold"),
    plot.caption = element_text(face = "italic", size = 10, color = "gray60"),
    legend.position = "none"
  )
```

There is an mix of a certain number of red and white beads with varying sizes in an urn of 1,000 beads. The data comes from an experiment simulating the urn, and there is a specific proportion of red beads to the total number of beads. The beads at the top, which the shovel can reach easily, might not be a good representative of a sample size. I model the probability that a bead is red, which takes values red or white, as a logistic function of the shovel sample data. The estimated average proportion of red beads is around 34%, and the true proportion for a 95% confidence interval is around 21% to 47%.
